APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-25 paper.tex
Write post processing section.

\title{APPM 3310 Project\\\Large{Static Analysis of Truss Systems}}
\author{Sammy Chang\and{}Ryan Marizza\and{}Michael Shannon}
\date{Friday, April 29, 2016}

@@

>>>>

\title{APPM 3310 Project\\\Large{Static Analysis of Truss Systems}}
\author{Sammy Chang\and{}Ryan Marizza\and{}Michael Shannon}
\date{Section: 002\\\vspace{1em}Friday, April 29, 2016}

@@

While the deformation for the truss is known at this point the stresses in the
elements are the desired quantity to determine if the goal is to determine if
the truss will break.  The first step is to find the change in length of each
element.  This is done by extracting the displacement values from $\mathbf{u}$
for each element reforming each $\mathbf{u}^e$.
Eq.~(\ref{eq:global_to_local}) is then used to move the displacement back into
the element local coordinate frame.  At this point only the two x-coordinate
displacement values (at each end of the element) are nonzero as an element can
only deform along its axis (given the simplifications used in this paper).
Subtracting one from the other gives the change in length
\parencite{felippa2004ch3}:
\begin{equation}
    d^e=\overline{\mathbf{u}}^e_{xj}-\overline{\mathbf{u}}^e_{xi}
\end{equation}
where $j$ is the 2nd node of the element and $i$ is the first.  Using this
result the longitudinal stress and force in the element is given by:
\begin{equation}
    \sigma^e=\frac{E^e}{L^e}d^e,\qquad
    F^e=\sigma^eA^e
\end{equation}
At this point, both the truss deformation and element stresses are known and
therefore the figures shown in this paper can be plotted.
